Cooperative Kernels: Safe Multitasking for Blocking Algorithms on GPUs

### 2016-11-13 write-ups/PLDI/paper.tex
Some related work text.

>>>>

\paragraph{Irregular algorithms and persistent kernels}
%
There has been a lot of work on accelerating blocking irregular
algorithms using GPUs~\cite{...}, and on the \emph{persistent threads}
programming style for long-running kernels.  These approaches rely on
the occupancy-bound execution model, and aim to take ownership of the
GPU by scheduling as many workgroups as the GPU has compute units,
relying on fair scheduling between these workgroups.  These approaches
render the GPU unavailable for other tasks, and are not future-proof
because (as discussed throughout the paper) the occupancy-bound
execution model is not guaranteed by GPU programming models and is
unlikely to be guaranteed in practice by future GPU platforms.

\ADComment{Now say that we could update these approaches to use cooperation.}
